Visual Interrogation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension

### 2018-05-30 EMNLP-demo-paper/conclusion.tex
shorten implementation
update result

\section{Discussion}
In this work, we introduce a visualization library for creating customized environments that allow the user to interrogate the relationship between different parts of the model pipeline via interactive queries.
%
We demonstrate the usability and flexibility of tool by configuring the visual components to investigate models for solving different NLP tasks (e.g., NLI, MC).
%
Due to the limited space, we didn't demonstrate all the available components, such as a visual summary of predict results of the entire development set, as well as a scheme to update the model based on user assigned prediction. 
%
We also conducted a small-scale user study, in which we ask several Ph.D. level student with NLP background to spend 30 minutes with the tool and provide feedback. The positive feedbacks mentioned the environment allow them to iteratively refine their queries and identify potential issues with the model, but some student also suggests the tool may not provide enough guidance for user do not have an in-depth understanding of the model.

We design the individual components with versatility in mind. Due to a large number of variants of attention networks, it is hard to ensure the current interface is compatible with all the available models.
%
In the future, we plan to expand the visualization component further to handle tasks such neural machine translation and more.

>>>>

\section{Discussion}
In this work, we introduce a visualization library for creating customized environments that allow the user to interrogate the relationship between different parts of the model pipeline via interactive queries.
%
We demonstrate the usability and flexibility of tool by configuring the visual components to investigate models for solving different NLP tasks (e.g., NLI, MC).
%
We also conducted a small-scale user evaluation, where we ask five Ph.D. level students with NLP background to spend 30 minutes with the tool and then provide feedback. Most suggest the environment allow them to refine queries iteratively and identify potential issues with the model, but some student also mentioned the tool might not provide enough guidance for user do not already have an in-depth understanding of the model at hand.

Even though we design the individual components with versatility in mind, due to a large number of variants of attention networks, it is hard to ensure the current interface is compatible with all the available configurations.
%
In the future, we plan to improve upon the current attention interface and expand the visualization component further to handle tasks such neural machine translation and more.

### 2018-05-30 EMNLP-demo-paper/result.tex
update result

\begin{figure*}[t]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{MC_interface}
  \vspace{-6mm}
 \caption{
The proposed visualization help reveal the potential alignment issues in the machine comprehension model.
The $p1$, $p2$ color bar illustrate the predicted start and end index for the answer (deeper the red the higher the probability).
The answer to the question is found in (a1), where the ``Two'' is aligned with the ``many'' in the question. However, the number 9 is also aligned with many, which may potentially lead to confusions.
The second best answer is illustrated in b2.
}
\label{fig:MCexample}
\end{figure*}

\subsection{Machine Comprehension}
\label{sec:MCexample}
In machine comprehension task, two sequences of texts are given: context/paragraph and question.
The goal is to select a span of text from the context that answers the question. 
%We provide a simple model formulation and refer the reader to the paper for details.
%%\begin{align}
%	$C^\prime, Q^\prime = BiLSTM(C), BiLSTM(Q)$,
%	$\overleftarrow{A} = u(C^\prime, Q^\prime)$,
%	$\overrightarrow{A} = v(C^\prime, Q^\prime)$,
%	$s = m(C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})$,
%	$e = n(s, C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})$,
%%\end{align}
%where $C$ and $Q$ are embedding matrices for the context and the question,
%$\overleftarrow{A}$ and $\overrightarrow{A}$ are bidirectional attention flows,
%$s$ and $e$ are probabilities for starting and ending indices of the answer span.
%Our system reveals the internal states of $\overleftarrow{A}$, $\overrightarrow{A}$,
%$s$ and $e$.
Similarly, the attention information is also encoded as a bi-directional alignment (i.e., from context to question and vice versa). 
The key difference is how the question to context alignment is computed (see \cite{Seo2016} for more details).
Here, we refer the context to question attention as \emph{att1}, and question to context attention as \emph{att2}.

>>>>

\begin{figure*}[t]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{MC_interface}
  \vspace{-6mm}
 \caption{
In the machine comprehension visualization interface (a), the $p1$, $p2$ color bar illustrate the predicted start and end index for the answer (deeper the red the higher the probability).
The answer to the question is found in (a1), where the ``Two'' is aligned with the ``many'' in the question. However, the number 9 is also aligned with many, which may potentially lead to confusions.
%
We can evaluate the robustness of the prediction by perturbing the question sentence (b1, b3). As illustrated in (b1, b2) by removing the word ``partial'' the model still find the correct answer (albeit different, as the sentence perturbation changes the exact meaning of the question). 
}
\label{fig:MCexample}
\end{figure*}

\subsection{Machine Comprehension}
\label{sec:MCexample}
In machine comprehension task, two sequences of texts are given: context/paragraph and question.
The goal is to select a span of text from the context that answers the question. 
%We provide a simple model formulation and refer the reader to the paper for details.
%%\begin{align}
%	$C^\prime, Q^\prime = BiLSTM(C), BiLSTM(Q)$,
%	$\overleftarrow{A} = u(C^\prime, Q^\prime)$,
%	$\overrightarrow{A} = v(C^\prime, Q^\prime)$,
%	$s = m(C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})$,
%	$e = n(s, C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})$,
%%\end{align}
%where $C$ and $Q$ are embedding matrices for the context and the question,
%$\overleftarrow{A}$ and $\overrightarrow{A}$ are bidirectional attention flows,
%$s$ and $e$ are probabilities for starting and ending indices of the answer span.
%Our system reveals the internal states of $\overleftarrow{A}$, $\overrightarrow{A}$,
%$s$ and $e$.
The attention information is encoded as a bi-directional alignment (i.e., from context to question and vice versa). 
%The key difference is how the question to context alignment is computed (see \cite{Seo2016} for more details).
Here, we refer the context to question attention as \emph{att1}, and question to context attention as \emph{att2} (the \emph{att2} is a vector instead of a matrix, see \cite{Seo2016} for more details).
